Training a Gaming Agent on Brainwaves

### 2020-08-19 ErrP.tex
Subo una nueva versión ya con todos los gráficos.
Subo algunos cambios adicionales.

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The central part is the retrieval of the observation human critic's brain activity.  This process is called brainwave session. Subjects are recruited voluntarily. They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data. The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years. All subjects have normal vision, are right-handed and have no history of neurological disorders.

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[scale=0.27]{Images/Average_steps/Ax.png}
\includegraphics[scale=0.27]{Images/Average_steps/Bx.png}
\end{subfigure}
\caption{(A) Average steps using Q-table trained with experiences from OHC 8 classified with a classifier trained with data from OHC 6.  (B) Average steps using Q-table trained with experiences from OHC 1 classified with a classifier trained with data from OHC 3.}
\label{fig:transferlearning}
\end{figure}

>>>>

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The central part is the retrieval of the OHC's brain activity.  This process is called brainwave session. Subjects are recruited voluntarily. They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data. The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years. All subjects have normal vision, are right-handed and have no history of neurological disorders.

@@

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
\end{subfigure}
\caption{(A) Average steps using Q-table trained with experiences from OHC 8 classified with a classifier trained with data from OHC 6.  (B) Average steps using Q-table trained with experiences from OHC 1 classified with a classifier trained with data from OHC 3.}
\label{fig:transferlearning}
\end{figure}
